### 2024-12-04 manuscript.tex
Update on Overleaf.

In general, sea surface temperature (SST) biases in the SO can originate either
in the atmosphere, caused by too much shortwave heating of the surface, too
little longwave cooling of the surface, or in the ocean circulation.
Interactions of both are also possible, for example SST affecting clouds and
clouds affecting the surface radiation. Using the European
Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference, \cite{zhang2023} have shown that SST
biases have improved in CMIP6 compared to CMIP5, with SST
overall increasing in the later CMIP phase. However, over the SO this resulted
in an even higher positive bias, especially in the Atlantic Ocean (AO) sector
of the SO, increasing by up to 1°C.  \cite{luo2023} identified that the SO SST
bias in an ensemble of 18 CMIP6 models originates not from the surface heat and
radiation fluxes (using reanalyses as a reference), but from a warm bias in the
Northern Atlantic Deep Water.

@@

Fig. \ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction
of cyclonic days as determined by the cyclone tracking algorithm applied to the
ERA5 reanalysis and ICON data (Section \ref{sec:cyclone-stability}). As
expected, the strongest cyclonic activity is in the high-latitude SO zone, and
it is relatively zonally symmetric at all latitudes.  While both reanalysis and
the model agree relatively well, there are clear differences particularly in the highest occurrence rate regions -- over the Amundsen Sea, where the Amundsen Sea low is located \cite{turner2013} and which is
more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic
in ICON. These differences might, however, stem from the relatively short time
periods of comparison (4 years) and the fact that the model is free-running.

@@

The relationship between cloud biases and radiation has a number of notable
features. Perhaps unsurprisingly, the reanalyses exhibit the too few, too
bright bias previously identified in models. In our results, this is
characterised by outgoing TOA SW radiation similar to or higher than in the
satellite observations, while at the same time total cloud fraction is
substantially underestimated relative to the ground-based lidar observations.
This feature seems to be much more pronounced in ERA5 than in MERRA-2. On the
other hand, this relationship is not present in ICON. This model generally
predicts smaller outgoing TOA SW radiation and smaller total cloud fraction
than observations, and the deficit of outgoing TOA SW radiation is
approximately proportional to the deficit of the total cloud fraction. While this
might be a welcome feature and an improvement over previous models, it does
mean that the outgoing TOA SW radiation is overall underestimated instead of
being compensated by a higher cloud albedo. This can, of course, lead to
undesirable secondary effects such as overestimated solar heating of the sea
surface, among other factors responsible for SO SST biases in climate models
\citep{zhang2023,luo2023}.

>>>>

In general, sea surface temperature (SST) biases in the SO can originate either
in the atmosphere \citep{hyder2018}, caused by too much shortwave heating of the surface, too
little longwave cooling of the surface, or in the ocean circulation.
Interactions of both are also possible, for example SST affecting clouds and
clouds affecting the surface radiation. Using the European
Centre for Medium-Range Weather Forecasts (ECMWF) Reanalysis 5 (ERA5) as a reference, \cite{zhang2023} have shown that SST
biases have improved in CMIP6 compared to CMIP5, with SST
overall increasing in the later CMIP phase. However, over the SO this resulted
in an even higher positive bias, especially in the Atlantic Ocean (AO) sector
of the SO, increasing by up to 1°C.  \cite{luo2023} identified that the SO SST
bias in an ensemble of 18 CMIP6 models originates not from the surface heat and
radiation fluxes (using reanalyses as a reference), but from a warm bias in the
Northern Atlantic Deep Water.

@@

Fig. \ref{fig:cyclone-stability}a, b show a geographical distribution of the fraction
of cyclonic days as determined by the cyclone tracking algorithm applied to the
ERA5 reanalysis and ICON data (Section \ref{sec:cyclone-stability}). As
expected, the strongest cyclonic activity is in the high-latitude SO zone, and
it is relatively zonally symmetric at all latitudes.  The pattern matches reasonably well with \cite{hoskins2005}. While both reanalysis and
the model agree relatively well, there are clear differences particularly in the highest occurrence rate regions -- over the Amundsen Sea, where the Amundsen Sea low is located \cite{turner2013} and which is
more cyclonic in the reanalysis, and around Cape Adare, which is more cyclonic
in ICON. These differences might, however, stem from the relatively short time
periods of comparison (4 years) and the fact that the model is free-running.

@@

The relationship between cloud biases and radiation has a number of notable
features. Perhaps unsurprisingly, the reanalyses exhibit the too few, too
bright bias previously identified in models. In our results, this is
characterised by outgoing TOA SW radiation similar to or higher than in the
satellite observations, while at the same time total cloud fraction is
substantially underestimated relative to the ground-based lidar observations.
This feature seems to be much more pronounced in ERA5 than in MERRA-2. On the
other hand, this relationship is not present in ICON. This model generally
predicts smaller outgoing TOA SW radiation and smaller total cloud fraction
than observations, and the deficit of outgoing TOA SW radiation is
approximately proportional to the deficit of the total cloud fraction. While this
might be a welcome feature and an improvement over previous models, it does
mean that the outgoing TOA SW radiation is overall underestimated instead of
being compensated by a higher cloud albedo. This can, of course, lead to
undesirable secondary effects such as overestimated solar heating of the sea
surface, among other factors responsible for SO SST biases in climate models
\citep{zhang2023,luo2023,hyder2018}.
